\documentclass[12pt]{book}
\usepackage{epsf}
\usepackage{graphicx}

\input{settings}

\begin{document}

\beforepreface

\prefacesection{2009 Sponsors}
We thank this year's sponsors:
\begin{itemize}

\item {\bf MIT Department of Electrical Engineering and Computer Science}\\
Financial funding, laboratory facilities, staff help and support.

\item {\bf MIT Copy Technology Centers}\\
Copying.

\item {\bf 3M}\\
Technical support.

\item {\bf Akamai}\\
Financial funding.

\item {\bf Analog Devices}\\
MEMs gyros and technical support.

\item {\bf Broadway Technology}\\
Financial funding.

\item {\bf DE Shaw}\\
Financial funding.

\item {\bf GM}\\
Financial funding.

\item {\bf Google}\\
Financial funding.

\item {\bf Guidant Foundation}\\
Financial funding.

\item {\bf Intempco}\\
Gyro Interface Board.

\item {\bf Jump Trading}\\
Prizes for our top competitors.

\item {\bf LEGO Dacta A/S, PITSCO}\\
PITSCO LEGO packs.

\item {\bf LEGO Denmark}\\
Bulk LEGO.

\item {\bf LEGO Shop-at-Home}\\
LEGO boxed sets.

\item {\bf Lockheed Martin}\\
Financial funding.

\item {\bf Microsoft}\\
Financial funding

\item {\bf Oracle}\\
Financial funding

\item {\bf QRST's}\\
T-shirts

\item {\bf Schlumberger}\\
Financial funding

\item {\bf Sharp Electronics}\\
Distance sensors

\end{itemize}

And we extend our special thanks to:
\begin{itemize}

\item {\bf Ron Roscoe and the 38-600 lab staff}\\
For infinite patience and invaluable resources.

\item {\bf Anne Hunter and the Course 6 Undergraduate Office}\\
A logistical powerhouse without whom we would truly be lost.

\contents
\afterpreface

\end{itemize}

 \input{intro.tex}

% Contest
 \input{contest.tex}
 \input{rules.tex}

% Assembly Manual
\input{assembly.tex}

% Sensor Design
\input{sensor.tex}

% Robot Construction
\input{constr.tex}

% Robot Control
\input{control.tex}

%\appendix
% IC appendix
%\input{icappendix.tex}

% Accellerometer appendix
%\input{accelappendix.tex}

% HB appendix
%\input{handy.tex}

\end{document}
