\section{The Competition}

The competition will be a double elimination tournament held over the
course of two days.  Robots compete head to head in successive rounds
until they lose twice.  When all but one robot has been eliminated,
that robot will be crowned champion.

This year, we have changed the way pairings are done in each round.
In each round, if there are an odd number of robots, the robot that
has scored the most cumulative points will face a placebo.  After that
robot is paired, the robot with the next highest cumulative score is
paired with the robot with the lowest cumulative score, and so forth.
Ties are resolved randomly.  Note that this system is only used for
deciding what opponent each robot will face -- the order in the round
and the side of the table are still randomly selected.

Every round of the competition is used for seeding -- two rounds on
Monday, two rounds on Thursday morning, and each round on Thursday
evening.

\begin{itemize}

\item {\bf Contest, Qualifying Rounds.}  The first two rounds of the
  contest serve as qualifying and seeding rounds.  If a robot
  demonstrates the ability to score points, regardless of whether it
  wins or loses, it will be allowed to proceed to the competition
  rounds on Thursday.  If it does not, modifications may be made, and
  it will have two more chances in lab to run against a
  non-competitive placebo.  If it cannot score points against the
  placebo after two tries, it will not qualify for the rest of the
  contest.  Losses to opponents during these rounds {\em do not} count
  towards a robot's elimination.

For the sake of efficiency, we will be publishing a schedule for the
  round matchups as soon as one is available.  We promise that each
  robot will not be asked to compete until the time that is posted.
  If a team is not present when we are ready to start the match, the
  team automatically forfeits.  This does not count against a team in
  elimination, only in seeding.

\item {\bf Contest, First and Second Rounds.}  Only qualifying robots
  may compete in the first and second rounds.  If a robot loses in
  both the first and second rounds, it will be eliminated from the
  competition.

For the sake of efficiency, we will be publishing a schedule for the
  round matchups as soon as one is available.  We promise that each
  robot will not be asked to compete until the time that is posted.
  If a team is not present when we are ready to start the match, the
  team automatically forfeits.  This {\em does} count against a team
  in elimination; if your team misses both of its starts, you will be
  eliminated from the competition.

\item {\bf Contest, Final Rounds.}  This is the main competition that
  everyone comes to see.  Robots will compete until all but the winner
  have been eliminated.  At the discretion of the Organizers, the
  final round of competition may be conducted in a round-robin format,
  ignoring previous losses.

\end{itemize}
