A short time from now, in a galaxy very close by, the masses are in unrest.

The non-trademark-infringing Gedi Knights Council, droid masters, guardians of the free world, and practitioners of the ancient interlocking plastic brick arts, have suffered a huge loss. Their former leader, Chin-wala-kane-ra, better known as "Chuck", has transcended to a higher plane of existence, and no longer will be around to keep the masses in check. An election will be held tonight to determine "Chuck's" replacement, for without a leader, the Gedi Knights will be powerless to stop the ever-growing threats of all-nighters in lab, freshman showering, and Red Sox fans.

Through many years of meditation and practice, the Gedi Knights have developed a keen ability to affect the subconsciouses of the weak-minded masses. These abilities, colloquially known as "mind tricks", are channeled and focused using autonomous mechanical contraptions, colloquially known as "robots". As part of their droid master training, each Gedi Knight shall build a robot companion and train it to serve as their vehicle for power and influence. 

Soon it will be Election Night. The robots will have only one mission - to influence as many votes as possible for thier Gedi Master. Faithful as an R2 unit and about as well trained as a womp rat, these robots shall be set in their tasks. Strength of will, speed of mind-tricks, and reliability of gear trains will be tested. And one droid shall triumph above all, ushering in a new era of leadership for the Gedi Council.

