In the far distant future, we find ourselves audience to a uniquely
MIT scene--Killian Kickoff.  It is the start of another school year,
and along with the morning newspaper, a new batch of freshmen have
arrived on campus.  As yet undecided to where they will live at
MIT--be it dorm, fraternity, sorority, or independent living
group--Rush is the time to make that decision.

Choices are numerous and time is short.  How does your living group
convince the freshmen to come live with you?  How does each living
group save itself from becoming the goose amongst the ducks?  Most of
all, how do you make sure the coolest freshmen live at your residence?
Cleaned, crisp, and endearingly naive, little do the freshmen suspect
the planning and strategizing that has gone on behind the scenes.

At Killian Kickoff, as the long awaited words are uttered, "Let the
Rush begin!" madness ensues as upperclassmen from each living group
sweep the freshmen off their feet and carry them away in Winnebagos
and Econovans.  But a small group of freshmen have set up defenses in
the center of Killian Court.  They are not to be picked up and taken
away like bags of rice, they will not be treated like cereal grains.
They stand tall and proud, until, far in the distance, they hear the
sound of whirring motors and distinctly offkey circus music.  Little
do they know that a new plan has been formed, and a new tactic
devised--the upperclassmen have decided to build robots to conquer the
freshmen.

In clouds of polyvinylchloride dust and soldering fumes, each living
group begins to assemble and design their robot.  These autonomous
robots are programmed with one goal in mind--to bring back as many
freshmen as possible to its living group.  Faithful as a golden
retriever and about as well trained as a tuna, these robots are set in
their task.  Nothing but flash photography will prevent these robots
from retrieving hapless freshmen.  Will your living group win over the
freshmen?  Will your robot succeed in bringing you the most victims
(ahem), freshmen?  Their young lives lay in your hands.  Build your
robots swift and strong.  Let the Rush begin!

